State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edited the abstract

\begin{abstract}
	This paper presents a framework for creating patient-specific neural field models from electrophysiological data. The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model. Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field. We use the reduced model to estimate the state and parameters of the non-reduced model. The estimation procedure consists of a two-stage algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation. The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework. The results also illustrate the cost of the model reduction with a loss of the high spatial frequency information. This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models. This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.   
\end{abstract}

@@

\begin{table*}

>>>>

\begin{abstract}
	This paper presents a framework for creating patient-specific neural field models from electrophysiological data. The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model. Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field. We use the reduced model to estimate the state and parameters of the full neural field model. The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation. The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant with the proposed framework. The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure. This framework provides a link between patient-specific neurophysiological data and theoretical neural fields models. This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.   
\end{abstract}

@@

\begin{table*}\footnotesize
